### 2013-09-26 structured_prediction/paper.tex
smallcaps for datasets, some more corrections by vlad

% TODO relate to computer vision here ??? Pairwise models?
% talk about inference?

@@

%TODO BMRM?

@@

Using superpixels instead of pixels has large computational advantages.  A
model that uses superpixels contains much fewer variables than one that works
on pixel-level.  Typical sizes for superpixels are in the hundereds of pixels,
leading to a hundred-fold decrease in the number of variables. There are also
semantic advantages. Using superpixels can constitute a form of regularization,
including prior knowledge about the structure of images. Modeling interactions
between superpixels also allows more distant parts of an image to interact,
instead of modeling long-term relations only indirectly over neighbors.
Finally, modeling decisions on a superpixel-level allows for more context for a
local decision, while semantic decisions on pixel-level are not meaningful near
object boundaries.  The main disadvantage of superpixel-based approaches is
that the initial oversegmentation can not be influenced by later reasoning.
This can be a problem if fine structures need to be segmented for which local
evidence does not suffice.
%
\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp_org}&%
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp}\\
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp_graph}&%
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp_gt}
\end{tabu}
\caption{%
    Schematic of CRFs over superpixels. From left to right: input image, superpixel segmentation
    using SLIC into about 100 superpixels, pairwise potential in the CRF, and desired labeling.
\figlabel{superpixel_illustration}}
\end{figure}

@@

\citet{szummer2008learning} on the other hand used a structured support vector
machine approach to learn unary and pairwise parameters. They use the classical
graph cut approach of \citet{boykov2001fast} for inference.  However, graph-cut
inference is only applicable to submular energies, and therefore severly
restricts the expressivity of the resulting model.
\citet{lucchi2011spatial} investigated the importance of global constraints,
using an approach similar to \citet{szummer2008learning}, but also learning
global interactions---however, these did not improve performance, compared to
simply including global descriptors into local classifiers.

@@

\subsection{Data, Features and Superpixels}
When evaluating learning algorithms in Chapter~\ref{ch:comparison} and
Chapter~\ref{ch:exact_learning} we use the well-established Pascal VOC 2010 and
MSRC-21 datasets, shown in the introduction in \Figref{pascal_msrc}.
As we focus on the learning algorithms in these chapters, we use features for
unary potentials from the literature.

For both datasets we use the TextonBoost class probablities provided by
\citet{krahenbuhl2012efficient}. For the Pascal VOC dataset, the potentials
provided by \citet{krahenbuhl2012efficient} also include the responses of
object detectors~\citet{}, to better capture the complex object classes.
We average the potentials inside superpixels and use the resulting feature
as input to our unary potentials.
For the MSRC-21 dataset, we compute TextonBoost on two different scales, as
suggested by \citet{mottaghianalyzing}. We additionally extract SIFT and color descriptors and create
bag-of-word descriptors for each superpixel. Following the approach of
\citet{lucchi2011spatial} we augment these with a global bag-of-word descriptor
for each image. We train a linear SVM using an approximation to the additive
$\chi^2$ kernel~\citet{vedaldi2010efficient} and use the response as an
additional input to our CRF\@. This \emph{piecewise training} simplifies
learning and was found to have little effect on
accuracy~\citet{nowozin2010parameter}. In total, there are $63$ features
for the MSRC-21 dataset, $21$ for each scale of TextonBoost and an additional
$21$ for the bag-of-word model using an SVM.

We use the SLIC~\citep{achanta2012slic} algorithm to create superpixel for all
our experiments.  It has been shown to provide competative results with a
minimum of computational complexity.  Algorithmically, SLIC simply computes a
$k$-means clustering over pixels. Each pixels is represented as 5D point, using
three color channels and the $x$ and $y$ coordinates in the image.  In a
post-processing step, small segments are removed. To make clustering of so many
points feasible, the search for the nearest cluster in $k$-means is restricted
to a local neighborhood in the image. An example of superpixels computed with the SLIC algorithm can be found in
\Figref{superpixel_illustration}.

>>>>

@@

@@

Using superpixels instead of pixels has large computational advantages.  A
model that uses superpixels contains much fewer variables than one that works
on pixel-level. Typical sizes for superpixels are in the hundreds of pixels,
leading to a hundred-fold decrease in the number of variables. There are also
semantic advantages. Using superpixels can constitute a form of regularization,
including prior knowledge about the structure of images. Modeling interactions
between superpixels also allows more distant parts of an image to interact,
instead of modeling long-term relations only indirectly over neighbors.
Finally, modeling decisions on a superpixel-level allows for more context for a
local decision, while semantic decisions on pixel-level are not meaningful near
object boundaries.  The main disadvantage of superpixel-based approaches is
that the initial over-segmentation can not be influenced by later reasoning.
This can be a problem if fine structures need to be segmented for which local
evidence does not suffice.
%
\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp_org}&%
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp}\\
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp_graph}&%
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp_gt}
\end{tabu}
\caption{%
    Schematic of CRFs over superpixels. From left to right: input image, superpixel segmentation
    using SLIC into about 100 superpixels, pairwise potential in the CRF, and desired labeling.
\figlabel{superpixel_illustration}}
\end{figure}

@@

\citet{szummer2008learning} on the other hand used a structured support vector
machine approach to learn unary and pairwise parameters. They use the classical
graph cut approach of \citet{boykov2001fast} for inference.  However, graph-cut
inference is only applicable to submodular energies, and therefore severely
restricts the expressiveness of the resulting model.
\citet{lucchi2011spatial} investigated the importance of global constraints,
using an approach similar to \citet{szummer2008learning}, but also learning
global interactions---however, these did not improve performance, compared to
simply including global descriptors into local classifiers.

@@

\subsection{Data, Features and Superpixels}
When evaluating learning algorithms in Chapter~\ref{ch:comparison} and
Chapter~\ref{ch:exact_learning} we use the well-established \textsc{Pascal} VOC 2010 and
MSRC-21 datasets, shown in the introduction in \Figref{pascal_msrc}.
As we focus on the learning algorithms in these chapters, we use features for
unary potentials from the literature.

For both datasets we use the TextonBoost class probabilities provided by
\citet{krahenbuhl2012efficient}. For the \textsc{Pascal} VOC dataset, the potentials
provided by \citet{krahenbuhl2012efficient} also include the responses of
object detectors~\citet{}, to better capture the complex object classes.
We average the potentials inside superpixels and use the resulting feature
as input to our unary potentials.
For the MSRC-21 dataset, we compute TextonBoost on two different scales, as
suggested by \citet{mottaghianalyzing}. We additionally extract SIFT and color descriptors and create
bag-of-word descriptors for each superpixel. Following the approach of
\citet{lucchi2011spatial} we augment these with a global bag-of-word descriptor
for each image. We train a linear SVM using an approximation to the additive
$\chi^2$ kernel~\citet{vedaldi2010efficient} and use the response as an
additional input to our CRF\@. This \emph{piecewise training} simplifies
learning and was found to have little effect on
accuracy~\citet{nowozin2010parameter}. In total, there are $63$ features
for the MSRC-21 dataset, $21$ for each scale of TextonBoost and an additional
$21$ for the bag-of-word model using an SVM.

We use the SLIC~\citep{achanta2012slic} algorithm to create superpixel for all
our experiments.  It has been shown to provide competitive results with a
minimum of computational complexity.  Algorithmically, SLIC simply computes a
$k$-means clustering over pixels. Each pixels is represented as 5D point, using
three color channels and the $x$ and $y$ coordinates in the image.  In a
post-processing step, small segments are removed. To make clustering of so many
points feasible, the search for the nearest cluster in $k$-means is restricted
to a local neighborhood in the image. An example of superpixels computed with
the SLIC algorithm can be found in \Figref{superpixel_illustration}.
